Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-25 paper.qmd
Added Projections for PaCMAP Gau

@@

five_gau_proj_pacmap_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55)) +
  interior_annotation("c", 
                      position = c(0.08, 0.9),
                      cex = 3)

# five_gau_proj_pacmap_model <- gen_proj_langevitour(
#   points_df = df_exe,
#   projection = projection,
#   edge_df = distance_df_small_edges |> select(-distance)
# ) +
#   xlim(c(-0.18, 0.1)) +
#   ylim(c(-0.78, -0.55))
```

@@

five_gau_proj_tsne_model + five_gau_proj_tsne_model +
  five_gau_proj_umap_model1 + five_gau_proj_umap_model2 +
  five_gau_proj_pacmap_model + five_gau_proj_pacmap_model +
  plot_layout(guides = "collect", ncol = 2) &
  theme(legend.position='none')
```

>>>>

## First projection
projection <- cbind(
    c(0.21889,-0.25701,-0.19529,-0.73412),
    c(-0.63168,0.27992,-0.42895,-0.17223))

@@

axis_scale <- limits/6
# axis_pos <- -2/3 * limits
axis_pos <- 0

five_gau_proj_pacmap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.05, 0.35)) +
  ylim(c(-0.05, 0.35)) +
  interior_annotation("e", 
                      position = c(0.08, 0.9),
                      cex = 3)

### Second projection
projection <- cbind(
    c(-0.60995,0.33361,0.32920,-0.31518),
    c(0.19525,-0.30554,0.74417,0.07600))

axis_scale <- limits/6
# axis_pos <- -2/3 * limits
axis_pos_x <- -0.05
axis_pos_y <- -0.4

adj <- function(x, axis_pos) axis_pos + x * axis_scale
axes <- data.frame(x1 = adj(0, axis_pos_x), 
                   y1 = adj(0, axis_pos_y), 
                   x2 = adj(projection[, 1], axis_pos_x), 
                   y2 = adj(projection[, 2], axis_pos_y))

theta <- seq(0, 2 * pi, length = 50)
circle <- data.frame(c1 = adj(cos(theta), axis_pos_x), 
                     c2 = adj(sin(theta), axis_pos_y))

five_gau_proj_pacmap_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.8,
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.1, 0.2)) +
  ylim(c(-0.45, 0)) +
  interior_annotation("f", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

five_gau_proj_tsne_model + five_gau_proj_tsne_model +
  five_gau_proj_umap_model1 + five_gau_proj_umap_model2 +
  five_gau_proj_pacmap_model1 + five_gau_proj_pacmap_model2 +
  plot_layout(guides = "collect", ncol = 2) &
  theme(legend.position='none')
```
